Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2022-10-28 analysis/paper/paper.Rmd
Reword model fitness descriptions

Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

>>>>

The fitness of all models was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
